% !TeX root = ../main.tex

\ustcsetup{
  keywords = {
    圈量子引力, 自旋网络, 费米子, 自旋泡沫
  },
  keywords* = {
    Loop Quantum Gravity, Spin-network,
    Fermion, Spinfoam
  },
}

\begin{abstract}
  圈量子引力是旨在探究当前理论物理学最重要的问题之一——量子引力问题的候选理论之一。近30年来，该理论得到了长足的发展。它遵循了广义相对论的基本原理，即微分同胚不变性及背景独立性，同时按照量子力学的形式构造量子理论。具体而言，圈量子引力通过将广义相对论重铸为一个规范理论，借鉴规范场量子化的方法，以和乐为基本变量将引力理论正则量子化，成功建立了量子引力的希尔伯特空间，并构造了几何量算符，推导出普朗克尺度下几何量具有分立本征值的物理图像。近年开始快速发展的协变圈量子引力，即自旋泡沫模型，是一种路径积分形式的量子引力，为正则圈量子引力的希尔伯特空间上动力学的定义提供了新的思路。
  
  本文分为三个部分，前两部分是对正则圈量子引力及协变圈量子引力的综述，力求运用本科的量子力学与广义相对论及相关数学的基础将圈量子引力的基本理论阐述清楚。第三部分即最后一章考察了圈量子引力与费米子的耦合，证明了该模型具有正确的半经典极限。
\end{abstract}

\begin{enabstract}
  Loop quantum gravity is one of the candidate theories aimed at exploring one of the most important problems in current theoretical physics -- quantum gravity. In the past 30 years, the theory has been greatly developed. It follows the basic principles of general relativity, that is, diffeomorphism invariance and background independence, while constructing quantum theory in the form of quantum mechanics. Specifically, loop quantum gravity has successfully established the Hilbert space of quantum gravity by recasting general relativity into a gauge theory, and using holonomy as the basic variable to quantize of gravity theory as in Yang-Mills gauge theory. Loop quantum gravity has constructed geometry operators and gives a physical picture with discrete eigenvalues of geometrical quantities at the Planck scale. In recent years, covariant loop quantum gravity, that is, the spin foam model, which is a quantum gravity theory in the form of path integrals, has made a rapid development, which provides new ideas for the definition of the dynamics on canonical loop quantum gravity Hilbert space.
  
  
  This thesis is divided into three parts. The first two parts are an overview of the canonical loop quantum gravity and covariant loop quantum gravity (spinfoam model). The aim of this thesis is trying to state the basic theoretical frame clearly based on the skills of quantum mechanics , general relativity and math that have been trained during the undergraduate education. The third part is the final chapter, which states the coupling of loop quantum gravity and fermions, and proves that the model has the correct semiclassical limit.

\end{enabstract}
